### 2021-08-27 ms/ms.Rmd
removed within taxon duplicates

# Methods

@@

@@

>>>>

# Materials and Methods

@@

# Acknowledgements

CDM designed the study, compiled data, analyzed data, and wrote the manuscript with input from all authors. All authors contributed data. We thank Jacob Watts for comments on earlier versions of this manuscript.

# Data avaibility

The final data set and phylogeny used in the analysis are included in the [Supporting Information]. The raw anatomical data and source code will be archived on Zenodo upon publication.

@@

```{r}

# write supporting information table
write_csv(pair_div, "ms/tableS2.csv")

### 2021-08-27 ms/ms.tex
removed within taxon duplicates

\begin{itemize}
\tightlist
\item
  Developmental integration can cause traits to covary over macroevolutionary time and in some cases prevent populations from reaching their adaptive optima. Developmental integration between stomatal size and density may contribute to two major features of stomatal anatomical evolution: inverse size-density scaling and bimodal stomatal ratio. If these patterns result from developmental integration, we predicted that in amphistomatous leaves 1) stomatal size and density should covary similarly on both abaxial and adaxial surfaces and 2) stomatal traits (size and density) on each surface should covary isometrically.
\item
  We synthesized data on stomatal density and length from amphistomatous leaves of 752 terrestrial seed plant taxa mostly from the literature. We estimated the covariance in divergence between stomatal traits from 329 phylogenetically independent contrasts using a robust Bayesian model.
\item
  Adaxial stomatal density, but not length, is evolutionary labile and not strongly integrated with stomatal length or abaxial stomatal density. Hence, developmental integration alone cannot explain inverse size-density scaling nor bimodal stomatal ratio.
\item
  Quasi-independent evolution of stomatal anatomical traits facilitates largely unfettered access to fitness optima. If stomatal anatomical traits are near their current fitness optimum, this implies that limits on trait (co)variance result from selective rather than developmental constraints. However, we cannot rule out that developmental integration is important in some lineages. Future research should identify the mechanistic basis of (dis)integration in stomatal development.
\end{itemize}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

We used the R packages \textbf{taxonlookup} version 1.1.5 (\protect\hyperlink{ref-pennell_simple_2016}{Pennell, FitzJohn, and Cornwell 2016}) and \textbf{V.phylomaker} version 0.1.0 (\protect\hyperlink{ref-jin_vphylomaker_2019}{Jin and Qian 2019}) to maximize overlap between our data set and the GBOTB.extended mega-tree of seed plants (\protect\hyperlink{ref-smith_constructing_2018}{S. A. Smith and Brown 2018} ; \protect\hyperlink{ref-zanne_three_2014}{Zanne et al. 2014}). We further resolved large (\(\ge4\) taxa) polytomies in 30 clades with sufficient sequence data using \textbf{PyPHLAWD} version 1.0 (\protect\hyperlink{ref-smith_pyphlawd_2019}{S. A. Smith and Walker 2019}) in Python 3.8.2 (Python Software Foundation, \url{https://www.python.org/}). We used sequence data from the most recent GenBank Plant and Fungal sequences database division (\protect\hyperlink{ref-ouellette_database_1997}{Ouellette and Boguski 1997}). We inferred subtree phylogenies using RAxML version 8.2.12 (\protect\hyperlink{ref-stamatakis_raxml_2014}{Stamatakis 2014}) and conducated molecular dating using the \texttt{chronos()} function in the R package \textbf{ape} version 5.5 (\protect\hyperlink{ref-paradis_ape_2019}{Paradis and Schliep 2019}) to obtain ultrametric trees. We grafted resolved, ultrametric subtrees onto the mega-tree at the polytomy nodes and rescaled to keep the mega-tree ultrametric. In some cases, resolving polytomies was not possible because there was little or no overlap between taxa in the data set and taxa with sequence data available for \textbf{PyPHLAWD}. In these cases, we randomly selected two taxa as a phylogenetially independent pair and dropped the rest. Remaining polytomies of three taxa were resolved randomly using the \texttt{multi2di()} function in \textbf{ape}. The final data set for which we had both trait and phylogenetic information contained 752 taxa. Seven taxa are gymnosperms; the vast majority are angiosperms.

@@

We extracted 329 phylogenetically independent taxon pairs. A fully resolved, bifurcating four-taxon phylogeny can have two basic topologies: \(\tt{((A,B),(C,D))}\) or \(\tt{((A,B),C),D))}\). Taxon pairs include all comparisons of \(\tt{A}\) with \(\tt{B}\) and \(\tt{C}\) with \(\tt{D}\) in each four-taxon clade. We extracted pairs using the \texttt{extract\_sisters()} function in R package \textbf{diverge} version 2.0.1 (\protect\hyperlink{ref-anderson_diverge_2021}{Anderson and Weir 2021}) and custom scripts (see source code). Taxon pairs are the most closely related pairs in our data set, but not usually the most closely related species in nature. For each pair we calculated phylogenetically independent contrasts (\protect\hyperlink{ref-felsenstein_phylogenies_1985}{Felsenstein 1985}) as the difference in the log\(_{10}\)-transformed trait value. Contrasts are denoted as \(\Delta \text{log(trait)}\). We log-transformed traits for normality because like many morphological and anatomical traits they are strongly right-skewed. Log-transformation also helps compare density and length, which are measured on different scales, because log-transformed values quantify proportional rather than absolute divergence. We only used pairs of terminal taxa rather than the entire tree for two reasons. First, even in whole-tree methods, approximately half of the data comes from divergence at the tips, so we do not lose much statistical power. Second, using a taxon-pair method obviates making strong assumptions about multivariate trait evolution process homogeneity throughout seed plant evolution. Homogeneity is biologically unlikely and it is difficult to fit more complex models reliably with only data from extant taxa.

@@

Stomatal length negatively covaries with stomatal density similarly on both surfaces, but on the adaxial surface there are many more taxa that have low stomatal density and small size compared to the abaxial surface (Fig. \ref{fig:h1_raw}). In principle, this pattern could arise either because size-density covariance differs or the variance in adaxial stomatal density increases faster than that for abaxial stomatal density. Also note that the interspecific variance increases with time since divergence for all traits (Table \ref{table:model_output}), but the covariance matrix structure did not change qualitatively over time (results not shown). For consistency, we therefore report estimates conditional on time since divergence set to 0. Across pairs, we estimate that the covariance between size and density is similar. The median estimate is \(\text{Cov}[\Delta \text{log}(L_\text{ad}), \Delta \text{log}(D_\text{ad})] - \text{Cov}[\Delta \text{log}(L_\text{ab}), \Delta \text{log}(D_\text{ab})] = 1.95 \times 10^{-3}\), but 0 is within the range of uncertainty (95\% HPD interval \([-9.35 \times 10^{-4},5.56 \times 10^{-3}]\)). However the variance in adaxial stomatal density is significantly greater than the abaxial stomatal density {[}Fig. \ref{fig:h1}{]}). We estimate \(\text{Var}[\Delta \text{log}(D_\text{ad})]\) is \(2.50 \times 10^{-2}\) (95\% HPD interval \([7.39 \times 10^{-3},4.24 \times 10^{-2}]\)) greater than \(\text{Var}[\Delta \text{log}(D_\text{ab})]\). The variance in stomatal length was similar for both surfaces, with an estimate of \(-6.36 \times 10^{-5}\) (95\% HPD interval \([-1.23 \times 10^{-3},9.92 \times 10^{-4}]\)).

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../figures/h1-raw.pdf}
\caption{Inverse size-density scaling in a synthesis of amphistomatous leaf traits across 752 taxa. The panels show the relationship between stomatal length ($x$-axis) and stomatal density ($y$-axis) on a log-log scale for values measured on the abaxial leaf surface (left) and the adaxial leaf surface (right). To avoid overplotting of points, we used a hexbin plot in which the shade of the hexagonal bin indicates the number of points in that bin. Whiter shades indicate more points (see scale to the right).}
\label{fig:h1_raw}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../figures/h1.pdf}
\caption{Evolutionary divergence in adaxial stomatal density is more variable, but covariance between density and length is similar on both surfaces. (a) Data from 329 phylogenetically independent contrasts of change in log(stomatal length) ($x$-axis) and log(stomatal density) ($y$-axis) for abaxial (left panel) and adaxial (right panel) leaf surfaces. Each contrast is shown by black points and every contrast appears on both panels. Grey ellipses are the model-estimated 95\% covariance ellipses. The negative covariance is similar for both surfaces but the breadth in the $y$-direction is larger for adaxial traits, indicating greater evolutionary divergence in log(stomatal density). (b) Parameter estimates (points), 66\% (thick lines), and 95\% HPD intervals for estimates of trait (co)variance. Grey points and lines represent ab- and adaxial values; black points and lines represent the estimated difference in (co)variance between surfaces. Only the variance for stomatal density (middle panel) is significantly greater for the adaxial surface (95\% HPD interval does not overlap the dashed line at 0). Reported paremeter estimates are conditioned on zero time since divergence between taxa (see \protect\hyperlink{results}{Results}).}
\label{fig:h1}
\end{figure}

@@

The relationship between stomatal density on each leaf surface is visually more variable than that for stomatal length (Fig. \ref{fig:h2_raw}). This pattern occurs because the slope and strength of integration for stomatal density on each surface is much weaker than that for stomatal length. The SMA slope between \(\Delta \text{log}(D_\text{ad})\) and \(\Delta \text{log}(D_\text{ab})\) is less than 1 (estimated slope \(= 0.804\), 95\% HPD interval \([0.699,0.919]\)) and the strength of association is weakly positive (estimated \(r^2 = 0.159\), 95\% HPD interval \([0.0832,0.24]\); Fig. \ref{fig:h2}). In contrast, the relationship between \(\Delta \text{log}(L_\text{ad})\) and \(\Delta \text{log}(L_\text{ab})\) is isometric (estimated slope \(= 1\), 95\% HPD interval \([0.94,1.07]\)) and strongly positive (estimated \(r^2 = 0.757\), 95\% HPD interval \([0.701,0.807]\); Fig. \ref{fig:h2}).

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../figures/h2-raw.pdf}
\caption{Relationship stomatal density and length on each leaf surface in a synthesis of amphistomatous leaf traits across 752 taxa. The panels show the relationship between the abaxial trait value ($x$-axis) and the adaxial trait value ($y$-axis) on a log-log scale for stomatal density (left) and stomatal length (right). To avoid overplotting of points, we used a hexbin plot in which the shade of the hexagonal bin indicates the number of points in that bin. Whiter shades indicate more points (see scale to the right). The dashed line in across the middle is the 1:1 line for reference.}
\label{fig:h2_raw}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../figures/h2.pdf}
\caption{Developmental integration in stomatal length is much stronger than stomatal density between the surfaces of amphistomatous leaves (a) Data from 329 phylogenetically independent contrasts of change in the abaxial trait value ($x$-axis) against change in the adaxial trait value ($y$-axis) for log(stomatal density) ($x$-axis) and log(stomatal density) (left panel) and log(stomatal length) (right panel). Each contrast is shown by black points and every contrast appears on both panels. Dashed grey lines are 1:1 lines for reference. Solid grey lines and ribbon the fitted SMA slope and 95\% HPD interval. (b) The SMA slope (left panel) is significantly less than 1 (isometry, top dashed line) for density but very close to isometric for length. The coefficient of determination ($r^2$, right panel) is also much greater for length than density. The points are parameter estimates with 66\% (thick lines) and 95\% HPD intervals. Reported paremeter estimates are conditioned on zero time since divergence between taxa (see \protect\hyperlink{results}{Results}).}
\label{fig:h2}
\end{figure}

@@

We predicted that if abaxial and adaxial stomata are developmentally integrated then we should observe a strong, isometric relationship between trait divergence on each surface. Consistent with this prediction, divergence in stomatal length on each surface is isometric (SMA slope \(=\) 1) and strongly associated (\(r^2 =\) 0.757; Fig. \ref{fig:h2}). In contrast, divergence in stomatal density on each surface was not isometric (SMA slope \(=\) 0.804) and much less integrated (\(r^2 =\) 0.159; Fig. \ref{fig:h2}). Since average stomatal density on each surface can evolve quasi-independently, a wide variety of stomatal ratios are developmentally possible. Leaves are not ``forced'' to deploy identical stomatal development programs on each surface. Hence, the bimodal stomatal ratio pattern (\protect\hyperlink{ref-muir_making_2015}{Muir 2015}) is unlikely to be the result of developmental integration alone.

@@

>>>>

\begin{itemize}
\tightlist
\item
  Developmental integration can cause traits to covary over macroevolutionary time and in some cases prevent populations from reaching their adaptive optima. Developmental integration between stomatal size and density may contribute to two major features of stomatal anatomical evolution: inverse size-density scaling and bimodal stomatal ratio. If these patterns result from developmental integration, we predicted that in amphistomatous leaves 1) stomatal size and density should covary similarly on both abaxial and adaxial surfaces and 2) stomatal traits (size and density) on each surface should covary isometrically.
\item
  We synthesized data on stomatal density and length from amphistomatous leaves of 711 terrestrial seed plant taxa mostly from the literature. We estimated the covariance in divergence between stomatal traits from 327 phylogenetically independent contrasts using a robust Bayesian model.
\item
  Adaxial stomatal density, but not length, is evolutionary labile and not strongly integrated with stomatal length or abaxial stomatal density. Hence, developmental integration alone cannot explain inverse size-density scaling nor bimodal stomatal ratio.
\item
  Quasi-independent evolution of stomatal anatomical traits facilitates largely unfettered access to fitness optima. If stomatal anatomical traits are near their current fitness optimum, this implies that limits on trait (co)variance result from selective rather than developmental constraints. However, we cannot rule out that developmental integration is important in some lineages. Future research should identify the mechanistic basis of (dis)integration in stomatal development.
\end{itemize}

@@

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

@@

We used the R packages \textbf{taxonlookup} version 1.1.5 (\protect\hyperlink{ref-pennell_simple_2016}{Pennell, FitzJohn, and Cornwell 2016}) and \textbf{V.phylomaker} version 0.1.0 (\protect\hyperlink{ref-jin_vphylomaker_2019}{Jin and Qian 2019}) to maximize overlap between our data set and the GBOTB.extended mega-tree of seed plants (\protect\hyperlink{ref-smith_constructing_2018}{S. A. Smith and Brown 2018} ; \protect\hyperlink{ref-zanne_three_2014}{Zanne et al. 2014}). We further resolved large (\(\ge4\) taxa) polytomies in 30 clades with sufficient sequence data using \textbf{PyPHLAWD} version 1.0 (\protect\hyperlink{ref-smith_pyphlawd_2019}{S. A. Smith and Walker 2019}) in Python 3.8.2 (Python Software Foundation, \url{https://www.python.org/}). We used sequence data from the most recent GenBank Plant and Fungal sequences database division (\protect\hyperlink{ref-ouellette_database_1997}{Ouellette and Boguski 1997}). We inferred subtree phylogenies using RAxML version 8.2.12 (\protect\hyperlink{ref-stamatakis_raxml_2014}{Stamatakis 2014}) and conducated molecular dating using the \texttt{chronos()} function in the R package \textbf{ape} version 5.5 (\protect\hyperlink{ref-paradis_ape_2019}{Paradis and Schliep 2019}) to obtain ultrametric trees. We grafted resolved, ultrametric subtrees onto the mega-tree at the polytomy nodes and rescaled to keep the mega-tree ultrametric. In some cases, resolving polytomies was not possible because there was little or no overlap between taxa in the data set and taxa with sequence data available for \textbf{PyPHLAWD}. In these cases, we randomly selected two taxa as a phylogenetially independent pair and dropped the rest. Remaining polytomies of three taxa were resolved randomly using the \texttt{multi2di()} function in \textbf{ape}. The final data set for which we had both trait and phylogenetic information contained 711 taxa. Seven taxa are gymnosperms; the vast majority are angiosperms.

@@

We extracted 327 phylogenetically independent taxon pairs. A fully resolved, bifurcating four-taxon phylogeny can have two basic topologies: \(\tt{((A,B),(C,D))}\) or \(\tt{((A,B),C),D))}\). Taxon pairs include all comparisons of \(\tt{A}\) with \(\tt{B}\) and \(\tt{C}\) with \(\tt{D}\) in each four-taxon clade. We extracted pairs using the \texttt{extract\_sisters()} function in R package \textbf{diverge} version 2.0.1 (\protect\hyperlink{ref-anderson_diverge_2021}{Anderson and Weir 2021}) and custom scripts (see source code). Taxon pairs are the most closely related pairs in our data set, but not usually the most closely related species in nature. For each pair we calculated phylogenetically independent contrasts (\protect\hyperlink{ref-felsenstein_phylogenies_1985}{Felsenstein 1985}) as the difference in the log\(_{10}\)-transformed trait value. Contrasts are denoted as \(\Delta \text{log(trait)}\). We log-transformed traits for normality because like many morphological and anatomical traits they are strongly right-skewed. Log-transformation also helps compare density and length, which are measured on different scales, because log-transformed values quantify proportional rather than absolute divergence. We only used pairs of terminal taxa rather than the entire tree for two reasons. First, even in whole-tree methods, approximately half of the data comes from divergence at the tips, so we do not lose much statistical power. Second, using a taxon-pair method obviates making strong assumptions about multivariate trait evolution process homogeneity throughout seed plant evolution. Homogeneity is biologically unlikely and it is difficult to fit more complex models reliably with only data from extant taxa.

@@

Stomatal length negatively covaries with stomatal density similarly on both surfaces, but on the adaxial surface there are many more taxa that have low stomatal density and small size compared to the abaxial surface (Fig. \ref{fig:h1_raw}). In principle, this pattern could arise either because size-density covariance differs or the variance in adaxial stomatal density increases faster than that for abaxial stomatal density. Also note that the interspecific variance increases with time since divergence for all traits (Table \ref{table:model_output}), but the covariance matrix structure did not change qualitatively over time (results not shown). For consistency, we therefore report estimates conditional on time since divergence set to 0. Across pairs, we estimate that the covariance between size and density is similar. The median estimate is \(\text{Cov}[\Delta \text{log}(L_\text{ad}), \Delta \text{log}(D_\text{ad})] - \text{Cov}[\Delta \text{log}(L_\text{ab}), \Delta \text{log}(D_\text{ab})] = 2.66 \times 10^{-3}\), but 0 is within the range of uncertainty (95\% HPD interval \([-6.72 \times 10^{-4},6.79 \times 10^{-3}]\)). However the variance in adaxial stomatal density is significantly greater than the abaxial stomatal density {[}Fig. \ref{fig:h1}{]}). We estimate \(\text{Var}[\Delta \text{log}(D_\text{ad})]\) is \(2.64 \times 10^{-2}\) (95\% HPD interval \([8.40 \times 10^{-3},5.13 \times 10^{-2}]\)) greater than \(\text{Var}[\Delta \text{log}(D_\text{ab})]\). The variance in stomatal length was similar for both surfaces, with an estimate of \(-8.08 \times 10^{-5}\) (95\% HPD interval \([-1.38 \times 10^{-3},1.23 \times 10^{-3}]\)).

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../figures/h1-raw.pdf}
\caption{Inverse size-density scaling in a synthesis of amphistomatous leaf traits across 711 taxa. The panels show the relationship between stomatal length ($x$-axis) and stomatal density ($y$-axis) on a log-log scale for values measured on the abaxial leaf surface (left) and the adaxial leaf surface (right). To avoid overplotting of points, we used a hexbin plot in which the shade of the hexagonal bin indicates the number of points in that bin. Whiter shades indicate more points (see scale to the right).}
\label{fig:h1_raw}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../figures/h1.pdf}
\caption{Evolutionary divergence in adaxial stomatal density is more variable, but covariance between density and length is similar on both surfaces. (a) Data from 327 phylogenetically independent contrasts of change in log(stomatal length) ($x$-axis) and log(stomatal density) ($y$-axis) for abaxial (left panel) and adaxial (right panel) leaf surfaces. Each contrast is shown by black points and every contrast appears on both panels. Grey ellipses are the model-estimated 95\% covariance ellipses. The negative covariance is similar for both surfaces but the breadth in the $y$-direction is larger for adaxial traits, indicating greater evolutionary divergence in log(stomatal density). (b) Parameter estimates (points), 66\% (thick lines), and 95\% HPD intervals for estimates of trait (co)variance. Grey points and lines represent ab- and adaxial values; black points and lines represent the estimated difference in (co)variance between surfaces. Only the variance for stomatal density (middle panel) is significantly greater for the adaxial surface (95\% HPD interval does not overlap the dashed line at 0). Reported paremeter estimates are conditioned on zero time since divergence between taxa (see \protect\hyperlink{results}{Results}).}
\label{fig:h1}
\end{figure}

@@

The relationship between stomatal density on each leaf surface is visually more variable than that for stomatal length (Fig. \ref{fig:h2_raw}). This pattern occurs because the slope and strength of integration for stomatal density on each surface is much weaker than that for stomatal length. The SMA slope between \(\Delta \text{log}(D_\text{ad})\) and \(\Delta \text{log}(D_\text{ab})\) is less than 1 (estimated slope \(= 0.815\), 95\% HPD interval \([0.69,0.929]\)) and the strength of association is weakly positive (estimated \(r^2 = 0.131\), 95\% HPD interval \([0.0613,0.202]\); Fig. \ref{fig:h2}). In contrast, the relationship between \(\Delta \text{log}(L_\text{ad})\) and \(\Delta \text{log}(L_\text{ab})\) is isometric (estimated slope \(= 1\), 95\% HPD interval \([0.934,1.08]\)) and strongly positive (estimated \(r^2 = 0.763\), 95\% HPD interval \([0.707,0.816]\); Fig. \ref{fig:h2}).

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../figures/h2-raw.pdf}
\caption{Relationship stomatal density and length on each leaf surface in a synthesis of amphistomatous leaf traits across 711 taxa. The panels show the relationship between the abaxial trait value ($x$-axis) and the adaxial trait value ($y$-axis) on a log-log scale for stomatal density (left) and stomatal length (right). To avoid overplotting of points, we used a hexbin plot in which the shade of the hexagonal bin indicates the number of points in that bin. Whiter shades indicate more points (see scale to the right). The dashed line in across the middle is the 1:1 line for reference.}
\label{fig:h2_raw}
\end{figure}

\begin{figure}[ht]
\includegraphics[width=\textwidth]{../figures/h2.pdf}
\caption{Developmental integration in stomatal length is much stronger than stomatal density between the surfaces of amphistomatous leaves (a) Data from 327 phylogenetically independent contrasts of change in the abaxial trait value ($x$-axis) against change in the adaxial trait value ($y$-axis) for log(stomatal density) ($x$-axis) and log(stomatal density) (left panel) and log(stomatal length) (right panel). Each contrast is shown by black points and every contrast appears on both panels. Dashed grey lines are 1:1 lines for reference. Solid grey lines and ribbon the fitted SMA slope and 95\% HPD interval. (b) The SMA slope (left panel) is significantly less than 1 (isometry, top dashed line) for density but very close to isometric for length. The coefficient of determination ($r^2$, right panel) is also much greater for length than density. The points are parameter estimates with 66\% (thick lines) and 95\% HPD intervals. Reported paremeter estimates are conditioned on zero time since divergence between taxa (see \protect\hyperlink{results}{Results}).}
\label{fig:h2}
\end{figure}

@@

We predicted that if abaxial and adaxial stomata are developmentally integrated then we should observe a strong, isometric relationship between trait divergence on each surface. Consistent with this prediction, divergence in stomatal length on each surface is isometric (SMA slope \(=\) 1) and strongly associated (\(r^2 =\) 0.763; Fig. \ref{fig:h2}). In contrast, divergence in stomatal density on each surface was not isometric (SMA slope \(=\) 0.815) and much less integrated (\(r^2 =\) 0.131; Fig. \ref{fig:h2}). Since average stomatal density on each surface can evolve quasi-independently, a wide variety of stomatal ratios are developmentally possible. Leaves are not ``forced'' to deploy identical stomatal development programs on each surface. Hence, the bimodal stomatal ratio pattern (\protect\hyperlink{ref-muir_making_2015}{Muir 2015}) is unlikely to be the result of developmental integration alone.

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

CDM designed the study, compiled data, analyzed data, and wrote the manuscript with input from all authors. All authors contributed data. We thank Jacob Watts for comments on earlier versions of this manuscript.

\hypertarget{data-avaibility}{%
\section{Data avaibility}\label{data-avaibility}}

The final data set and phylogeny used in the analysis are included in the \protect\hyperlink{supporting-information}{Supporting Information}. The raw anatomical data and source code will be archived on Zenodo upon publication.
